### 2022-05-30 main/chapter_2ljets.tex
use subfigure for ewk; add some todos; some cleanup

\begin{figure}[t]
\centering
\includegraphics[width=0.48\textwidth]{figures/2ljets_c1n2_llqqn1n1_wz.pdf}
\hfill
\includegraphics[width=0.45\textwidth]{figures/2ljets_n1n1_hhggzz.pdf}
\caption{%
Supersymmetric signal processes in the $\twoljets$-electroweak
analysis.
\textit{Figures reproduced from the paper%
}~\cite{atlas2022searches, atlas_susy_feynman}.
\\[0.5em]
Left: C1N2, where the initial $\chargino_1\textrm{--}\neutralino_2$ pair
is produced through a $s$-channel $W^{\pm}$ resonance and the masses of
weak bosons in decays are bounded by the mass splitting
$m(\chargino_1, \neutralino_2) - m(\neutralino_1)$.
We explore the parameters
$m(\chargino_1, \neutralino_2)$ and $m(\neutralino_1)$.
\\[0.5em]
Right: GMSB, where the initial $\neutralino_1\textrm{--}\neutralino_1$ pair
is produced by soft decays from pairs including $\chargino_1$,
$\neutralino_2$ or $\neutralino_1$.
Although the $h$ and $Z$ bosons decay to many states, we target
$Z\rightarrow \ell\ell$ with
$h/Z\rightarrow bb/jj$.
We explore the parameters
$m(\neutralino_1)$ and $B(\neutralino_1 \rightarrow h \tilde{G})$ with fixed
$m(\chargino_1, \neutralino_2) - m(\neutralino_1) = 1\,\eV[G]$.
}
\label{fig:2ljets_signal_diagrams}
\end{figure}

@@

The $\twoljets$-strong search complements the search for strongly interacting
supersymmetric effects by including cases where their decays produce pairs
of charged leptons.
Like the RJR and electroweak parts, jets and invisible lightest supersymmetric
particles are also generated.

@@

% previous papers
% three signal models
\begin{figure}[t]
\centering
\begin{subfigure}{0.45\textwidth}
    \centering
    \includegraphics[width=\textwidth]{figures/2ljets_strong_gogo_qqqqllllN1N1_N2.pdf}
    \caption{gluino-slepton}
\end{subfigure}
\hfill
\begin{subfigure}{0.45\textwidth}
    \centering
    \includegraphics[width=\textwidth]{figures/2ljets_strong_gogo_qqqqZZN1N1.pdf}
    \caption{gluino-$Z^{(*)}$}
\end{subfigure}
\\[0.5em]
\begin{subfigure}{0.45\textwidth}
    \centering
    \includegraphics[width=\textwidth]{figures/2ljets_strong_sqsq_qqZZN1N1.pdf}
    \caption{squark-$Z^{(*)}$}
\end{subfigure}
\caption{%
Supersymmetric signal processes in the $\twoljets$-strong search.
\textit{Figures reproduced from the paper%
}~\cite{atlas2022searches, atlas_susy_feynman}.
\\[0.5em]
\TODO{expand{
}
\label{fig:2ljets_strong_signal_diagrams}
\end{figure}

@@

>>>>

\begin{figure}[t]
\centering
\begin{subfigure}{0.48\textwidth}
    \centering
    \includegraphics[width=\textwidth]{figures/2ljets_c1n2_llqqn1n1_wz.pdf}
    \caption{C1N2}
\end{subfigure}
\hfill
\begin{subfigure}{0.45\textwidth}
    \centering
    \includegraphics[width=\textwidth]{figures/2ljets_n1n1_hhggzz.pdf}
    \caption{GMSB}
\end{subfigure}
\caption{%
Supersymmetric signal processes in the $\twoljets$-electroweak
analysis.
\textit{Figures reproduced from the paper%
}~\cite{atlas2022searches, atlas_susy_feynman}.
\\[0.5em]
Left: C1N2, where the initial $\chargino_1\textrm{--}\neutralino_2$ pair
is produced through a $s$-channel $W^{\pm}$ resonance and the masses of
weak bosons in decays are bounded by the mass splitting
$m(\chargino_1, \neutralino_2) - m(\neutralino_1)$.
We explore the parameters
$m(\chargino_1, \neutralino_2)$ and $m(\neutralino_1)$.
\\[0.5em]
Right: GMSB, where the initial $\neutralino_1\textrm{--}\neutralino_1$ pair
is produced by soft decays from pairs including $\chargino_1$,
$\neutralino_2$ or $\neutralino_1$.
Although the $h$ and $Z$ bosons decay to many states, we target
$Z\rightarrow \ell\ell$ with
$h/Z\rightarrow bb/jj$.
We explore the parameters
$m(\neutralino_1)$ and $B(\neutralino_1 \rightarrow h \tilde{G})$ with fixed
$m(\chargino_1, \neutralino_2) - m(\neutralino_1) = 1\,\eV[G]$.
}
\label{fig:2ljets_signal_diagrams}
\end{figure}

@@

The $\twoljets$-strong search target strongly interacting supersymmetric effects in cases where their decays produce pairs
of charged leptons.
Like the RJR and electroweak parts, jets and invisible lightest supersymmetric
particles are also generated.

@@

% previous papers
% three signal models
\begin{figure}[t]
\centering
\begin{subfigure}{0.45\textwidth}
    \centering
    \includegraphics[width=\textwidth]{figures/2ljets_strong_gogo_qqqqllllN1N1_N2.pdf}
    \caption{gluino-slepton}
\end{subfigure}
\hfill
\begin{subfigure}{0.47\textwidth}
    \centering
    \includegraphics[width=\textwidth]{figures/2ljets_strong_gogo_qqqqZZN1N1.pdf}
    \caption{gluino-$Z^{(*)}$}
\end{subfigure}
\\[0.5em]
\begin{subfigure}{0.45\textwidth}
    \centering
    \includegraphics[width=\textwidth]{figures/2ljets_strong_sqsq_qqZZN1N1.pdf}
    \caption{squark-$Z^{(*)}$}
\end{subfigure}
\caption{%
Supersymmetric signal processes in the $\twoljets$-strong search.
\textit{Figures reproduced from the paper%
}~\cite{atlas2022searches, atlas_susy_feynman}.
\\[0.5em]
\TODO{expand}
}
\label{fig:2ljets_strong_signal_diagrams}
\end{figure}

@@

\TODO{data driven backgrounds: flavour symmetry, photon method z+jets, 40GeV cut}
